Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex

     \end{tikzpicture}
     \end{center}
  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm. 		
  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (drak blue).
  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii (8, 10, 16, 20)}
  \label{fig:timings}
\end{figure}

>>>>

     \end{tikzpicture}
     \end{center}
  \caption{Timings obtained while visualizing an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (dark blue).
  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii ($8$, $10$, $16$ and $20$)}
  \label{fig:timings}
\end{figure}
